%%% Author: mterenui (F.M.T. C)
%%% Docs: https://github.com/xxx
%%% License: GNU General Public License v3.0
%%% This document is provided as a general template for informational purposes only and does not constitute legal advice. Permission is granted to copy, modify, and use this template for personal or commercial purposes, provided that this copyright and license notice is retained in all copies or substantial portions of the document. The author makes no representations or warranties regarding the legal validity or enforceability of this template in any jurisdiction. Users are strongly encouraged to consult a qualified legal professional before using this document.

\section{Collateral}
\label{sec:collateral}

$\square$ \textbf{No Collateral}
This loan is unsecured.

\vspace{0.3cm}

\noindent $\square$ \textbf{With Collateral}
As security for the full and timely payment and performance of all obligations under this Promissory Note, the \textbf{\textit{Borrower}} hereby grants and pledges to the \textbf{\textit{Lender}} a continuing security interest in the collateral described below (“\textit{Collateral}”).

\subsection*{Description of Collateral}
The Collateral securing this Note consists of the following property, whether now owned or hereafter acquired:

\vspace{0.3cm}

\noindent
\begin{tabular}{p{6cm} p{10cm}}
\textbf{Description:} & \CollateralDescription{} \\ 
\textbf{Address:} & \CollateralAddress{} \\ 
\textbf{Country:} & \CollateralCountry{} \\ 
\textbf{Estimated Value:} & \CollateralEstimatedValue{} \\ 
\end{tabular}

\subsection*{Borrower Representations}
The \textbf{\textit{Borrower}} represents and warrants that:

\begin{itemize}
  \item The \textbf{\textit{Borrower}} is the lawful owner of the Collateral.
  \item The Collateral is free and clear of all liens, claims, and encumbrances, except as disclosed in writing to the \textbf{\textit{Lender}}.
  \item The \textbf{\textit{Borrower}} has full authority to grant this security interest.
\end{itemize}

\subsection*{Maintenance of Collateral}
The \textbf{\textit{Borrower}} agrees to:

\begin{itemize}
  \item Keep the Collateral in good condition and reasonable repair.
  \item Not sell, transfer, lease, or otherwise dispose of the Collateral without the prior written consent of the \textbf{\textit{Lender}}.
  \item Maintain any required insurance on the Collateral, naming the \textbf{\textit{Lender}} as loss payee, if applicable.
\end{itemize}

\subsection*{Perfection of Security Interest}
The \textbf{\textit{Borrower}} authorizes the \textbf{\textit{Lender}} to take any actions reasonably necessary to perfect and protect the \textbf{\textit{Lender}}’s security interest, including the filing of financing statements or other public notices as permitted by law.

\subsection*{Default and Remedies}
Upon an event of default, the \textbf{\textit{Lender}} shall have all rights and remedies available under this Note and applicable law, including but not limited to:

\begin{itemize}
  \item Taking possession of the Collateral without judicial process, where permitted by law.
  \item Selling, leasing, or otherwise disposing of the Collateral and applying the proceeds to the outstanding balance, including reasonable costs of enforcement.
  \item Pursuing any deficiency remaining after application of proceeds.
\end{itemize}

\subsection*{No Waiver}
The \textbf{\textit{Lender}}’s failure to exercise any right or remedy with respect to the Collateral shall not constitute a waiver of that or any other right.

%%% End of document (collateral.tex)